### 2019-09-23 conflog.tex
adds hotel info and jeremy bio

\subsection{Date Selection}
Primary date selection\\
Rationale for date selection\\
Graphical calendar of date selection and conflicts\\

We are aware that there is no perfect date in which everyone who wants to attend the conference can do so. However, our hope is to accommodate as many students as possible with a proposed date of either: Thursday April 8th - Saturday April 10th or Thursday April 15th - April 17th, 2021. Two dates are proposed because the Mom's association that runs Mom's Weekend, one of the largest events of the year, has not announced their 2021 dates yet. Mom's weekend is typically held the first weekend of April which conflicts with Easter in 2021. This consensus was reached after looking up any holidays, scheduled spring breaks, final exams, and other miscellaneous conflict dates for 42 schools with active ANS student sections. Based on these findings, there are no major conflicts with any of the schools for these dates. These factors were considered in order to maximize the possible number of attendees that can benefit from the conference. A handful of schools did not have an academic calendar available for the 2021 Spring semester, so data was based on their listed 2020 dates. These date selections avoid conflicting with large event weekends such as Mom's Weekend, dates pending, and the Illini Marathon. If, for some reason, an issue arises with our proposed dates, our back-up date is Thursday April 1st - Saturday April 3rd. This is unfortunately the same weekend as Easter Sunday. However, we prioritized avoid final exams, and UIUC’s Mom’s Weekend. Please see the appendix for the full conflicts calendar.

\subsection{Conference Facilities}
\begin{itemize}
  \item \textbf{The Illini Union}\\
  \item \textbf{National Center for Supercomputing Applications (NCSA)}\\
  \item \textbf{Beckman Institute}\\
  \item \textbf{The I-Hotel}\\
  \item \textbf{}\\
\end{itemize}

\subsection{Conference Contingency Plan}
\subsection{Hotels and Accomodations}

$\Large\textbf{Illini Union}$\\

$\Large\textbf{Marriott TowneSuites}$\\

$\Large\textbf{Hyatt}$\\

\subsection{Travel and Transportation}

\subsubsection{Getting to Champaign}
The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport. There is also a small airport located just 20 minutes outside of campus. Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day. Below are the round-trip, non-stop, airfare costs for the first weekend of April.  
\begin{center}
	\begin{tabular}{lcc}
		\hline\hline
		\textbf{School} & \textbf{Departure City} & \textbf{Airfare to O'Hare (ORD)*}\\
		\hline\hline
		University of Florida & Orlando (ORL) & $\$$ 236\\
		Texas A$\&$M & College Station (CLL)& $\$$ 393\\
		Penn State University & State College (SCE) & $\$$ 349\\
		MIT & Boston (BOS) & $\$$ 217\\
		UNLV & Las Vegas (LAS) & $\$$ 308\\
		Georgia Tech & Atlanta (ATL) & $\$$ 175\\
		University of Michigan & Detroit (DTW) & $\$$ 240\\
		Oregon State University & Portland (PDX) & $\$$ 355\\
		RPI & Albany (ALB) & $\$$ 504\\
		UC Berkley & Oakland (OAK) & $\$$ 674\\
		UC Irvine & Orange County (SNA) & $\$$ 439\\
		US Naval Academy & Baltimore (BWI)& $\$$ 383\\
		University of Marlyand & Baltimore (BWI) & $\$$ 383\\
		University of Missouri-Columbia & St. Louis (STL) & $\$$ 168\\
		University of Nevada & Reno (RNO) & $\$$ 374\\
		University of New Mexico & Albuqurque (ABQ) & $\$$ 477\\
		NC State  University & Raleigh (RDU) & $\$$ 195\\
		University of Pittsburgh& Pittsburgh (PIT) & $\$$ 271\\
		Clemson University & Greenville (GSP) & $\$$ 295\\
		SC State University & Columbia (CAE) & $\$$ 365\\
		University of South Carolina & Columbia (CAE) & $\$$ 365\\
		Brigham Young University & Salt Lake City (SLC) & $\$$ 441\\
		U. Wisconsin-Madison & Madison (MSN) & $\$$ 229\\
		Colorado School of Mines & Denver (DEN)& $\$$ 223\\
		University of  Tennessee-Knoxville & Knoxville (TYS) & $\$$ 279\\
		Virginia Commonwealth University & Richmond (RIC) & $\$$ 326 \\
		Iowa State University & Des Moines (DSM) & $\$$ 199 \\
		University of Iowa & Cedar Rapids (CID) & $\$$ 249 \\
	\end{tabular}	
\end{center}
\textbf{*}\textit{These fares are predicted to go down around February and March.}\\

@@

>>>>

\subsection{Date Selection}

We propose the conference be held on the following dates: 
\begin{enumerate}
	\item Thursday, April 8$^{th}$ - Sunday, April 11$^{th}$ 
	\item Thursday, April 15$^{th}$ - Sunday, April 18$^{th}$
\end{enumerate}
We believe either of these dates would serve as an appropriate first choice because they avoid major conflict dates like finals and spring break for most schools. Additionally, mid-April offers pleasant mild weather in Champaign. The reason for proposing two weekends to host the conference is due to the UIUC tradition of hosting Mom's Weekend on or near the first weekend in April. The Illinois Mom's Association has not yet announced their 2021 dates but to avoid potential conflict, we suggest two dates. In the event that both of these dates are unavailable our backup date is 
\begin{itemize}
	\item Thursday, April 1$^{st}$ - Sunday, April 4$^{th}$.  
\end{itemize}
This is a backup date because Easter falls on that Sunday. In general, this should be avoided. In this case we found that holding the conference at the end of April would conflict with finals for students and holding it earlier in March would conflict with several spring breaks as well as having potentially poorer weather. A detailed conflict schedule is listed in Appendix A.

\subsection{Conference Facilities}

\textbf{The Illini Union}\\

% \begin{figure}[h!]
% 	\includegraphics[width=\textwidth]{illini-union.png}
% 	\caption{Illini Student Union}
% \end{figure}

The Illini Union is capable of hosting the entire technical program. Keeping the conference contained in one convenient location while being within easy access of the rest of the campus. Technical sessions will be held in a combination of rooms on the second, third, and fourth floors of The Union. Each of these rooms has at least enough capacity for 42 people and A/V capability. There will also be rooms available to have panels and workshops during the course of the technical program. The Illini Rooms A and B will be a combined space for the career fair and Illini Room C will host the poster sessions. We will keep the space open to allow the poster sessions and career fairs to share attendance and encourage networking. A detailed list of room capacities and floor plans are located in Appendix D: Building Layout.

\subsection{Conference Contingency Plan}
In the event that the Union has reduced availability during the conference we have the ability to host technical sessions and workshops at a combination of buildings: The National Center for Supercomputing Applications (NCSA) and Beckman Institute. These two buildings have large capacity rooms and small capacity rooms. As these buildings are UIUC property, the cost of renting them are significantly reduced compared to a private facility. Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from either the Union or Marriott TowneSuites. See Fig.\ref{fig:conf-map} for a map of the proposed conference facilities.\\

\textbf{National Center for Supercomputing Applications (NCSA)}\\
NCSA is a hub of transdisciplinary research and digital scholarship where University of Illinois faculty, staff, and students, and collaborators from around the globe, unite to address research grand challenges for the benefit of science and society.\\
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{ncsa_front.jpg}
	\caption{NCSA}
	\label{fig:ncsa}
\end{figure}

\textbf{Beckman Institute}
The Beckman Institute for Advanced Science and Technology at the University of Illinois is an interdisciplinary research institute devoted to leading-edge research in the physical sciences, computation, engineering, biology, behavior, cognition, and neuroscience.\\

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{beckman.jpg}
	\caption{Beckman Institute}
	\label{fig:beckman}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{campus_map.png}
	\caption{Map of conference facilities and hotels}
	\label{fig:conf-map}
\end{figure}

\subsection{Hotels and Accomodations}
We are fortunate to have our primary hotel, the Union, be the same as our primary conference venue. While the Union has many rooms available it does not have enough capacity to hold every attendee of the conference. Thus, we have listed two hotels that are on campus and can house the majority of attendees plus a third hotel where professionals and overflow attendees can stay.

$\textbf{Illini Union}$\\
This is the primary hotel for all student attendees and invited speakers.Commuting to the conference will be as easy as taking the elevator downstairs because the Illini Union is where the primary conference activities will be held. The Union is also a five-minute walk from Green Street, the campus hub of dining and social activities. Guests have access to Wi-Fi and, upon request, guest passes to the university recreational facilities. Breakfast is provided in the form vouchers for any of the hotel restaurant options inside the Union. Hosting technical sessions, workshops, and plenaries in the Union will help us negotiate a lower room rate.\\

$\textbf{Marriott TowneSuites}$\\
Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave, dishes, and dining area. Many rooms are equipped with pull-out couches, allowing 5 students to share a queen double room if desired. The hotel offers internet access for a maximum of 3 devices per room. The hotel is located on Green Street and the Illini Union a mere five-minute walk away. For $\$$7 a day, guests may park in a parking garage with 8ft clearance.

% \begin{figure}[H]
% \centering
% \begin{subfigure}{0.5\linewidth}
% 	\includegraphics[width=0.4\textwidth]{marriott_room1.jpeg}		
% \end{subfigure}
% \end{figure}
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.5\linewidth}
		\centering
		\includegraphics[width=0.5\textwidth]{marriott_room1.jpeg}
		\caption{Marriott queen double}
	\end{subfigure}
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.5\textwidth]{marriott_room2.jpeg}
		\caption{Marriott king single}
	\end{subfigure}
\end{figure}

$\textbf{Hyatt}$\\
The Hyatt is a gorgeous hotel located in the heart of downtown Champaign, surrounded by local restaurants and vibrant a nightlife. It is just a short busride away from the main conference activities. Parking is also available for added accessibility. This is a great place for professionals to stay and enjoy. Wifi is included with every room. Joining the Hyatt rewards program is free and comes with the added benefit of free breakfast every morning.

\newpage
\subsection{Travel and Transportation}

\subsubsection{Getting to Champaign}
The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport. There is also a small airport located just 20 minutes outside of campus. Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day. Below are the round-trip, non-stop, airfare costs for the first weekend of April. Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip.   
\begin{center}
	\begin{tabular}{lcc}
		\hline\hline
		\textbf{School} & \textbf{Departure City} & \textbf{Airfare to O'Hare (ORD)*}\\
		\hline\hline
		University of Florida & Orlando (ORL) & $\$$ 236\\
		Texas A$\&$M & College Station (CLL)& $\$$ 393\\
		Penn State University & State College (SCE) & $\$$ 349\\
		MIT & Boston (BOS) & $\$$ 217\\
		UNLV & Las Vegas (LAS) & $\$$ 308\\
		Georgia Tech & Atlanta (ATL) & $\$$ 175\\
		University of Michigan & Detroit (DTW) & $\$$ 240\\
		Oregon State University & Portland (PDX) & $\$$ 355\\
		RPI & Albany (ALB) & $\$$ 504\\
		UC Berkley & Oakland (OAK) & $\$$ 674\\
		UC Irvine & Orange County (SNA) & $\$$ 439\\
		US Naval Academy & Baltimore (BWI)& $\$$ 383\\
		University of Marlyand & Baltimore (BWI) & $\$$ 383\\
		University of Missouri-Columbia & St. Louis (STL) & $\$$ 168\\
		University of Nevada & Reno (RNO) & $\$$ 374\\
		University of New Mexico & Albuqurque (ABQ) & $\$$ 477\\
		NC State  University & Raleigh (RDU) & $\$$ 195\\
		University of Pittsburgh& Pittsburgh (PIT) & $\$$ 271\\
		Clemson University & Greenville (GSP) & $\$$ 295\\
		SC State University & Columbia (CAE) & $\$$ 365\\
		University of South Carolina & Columbia (CAE) & $\$$ 365\\
		Brigham Young University & Salt Lake City (SLC) & $\$$ 441\\
		U. Wisconsin-Madison & Madison (MSN) & $\$$ 229\\
		Colorado School of Mines & Denver (DEN)& $\$$ 223\\
		University of  Tennessee-Knoxville & Knoxville (TYS) & $\$$ 279\\
		Virginia Commonwealth University & Richmond (RIC) & $\$$ 326 \\
		Iowa State University & Des Moines (DSM) & $\$$ 199 \\
		University of Iowa & Cedar Rapids (CID) & $\$$ 249 \\
	\end{tabular}	
\end{center}
\textbf{*}\textit{These fares are predicted to go down around February and March.}\\

@@

\subsubsection{Getting to the Conference}
The primary location for all conference events is the Illini Union. This is also the primary hotel for conference attendees. The secondary hotel, Marriott TowneSuites is merely a five minute walk from the Union.

### 2019-09-23 management.tex
adds hotel info and jeremy bio

\setlength\intextsep{0pt}
\begin{wrapfigure}{L}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[width=0.3\textwidth]{dotsons2.jpg}
	\end{center}
\end{wrapfigure}
$\textbf{General Co-Chair - Sam Dotson}$\\
Sam graduated with a B.S. in Physics from UIUC in 2019. He attended his first ANS student conference in April 2019 and was so inspired by his experience that he decided to pursue graduate work in nuclear engineering rather than physics. Now he does research on machine learning applications and computational reactor physics with Dr. Kathryn Huff in the ARFC group. Hosting a student conference that will inspire others the way he was inspired is one of his top priorities this year. He has experience planning activities for student organizations such as Guidance for Physics Students (GPS) and has experience fundraising for the College of Lake County (CLC). He helped set a record amount of donations at the 2016 CLC Foundation Gala, where he was an invited speaker and volunteer. He will be attending the ANS National conference in November 2019, as well as the ANS Student Conference 2020 at North Carolina State University.\\

$\textbf{Technical Co-Chair - Jeremy Mettler}$\\

>>>>

\setlength\intextsep{0pt}
\begin{wrapfigure}{L}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[height=15\baselineskip]{dotsons2.jpg}
	\end{center}
\end{wrapfigure}
$\textbf{General Co-Chair - Sam Dotson}$\\
Sam graduated with a B.S. in Physics from UIUC in 2019. He attended his first ANS student conference in April 2019 and was so inspired by his experience that he decided to pursue graduate work in nuclear engineering rather than physics. Now he does research on machine learning applications and computational reactor physics with Dr. Kathryn Huff in the ARFC group. Hosting a student conference that will inspire others the way he was inspired is one of his top priorities this year. He has experience planning activities for student organizations such as Guidance for Physics Students (GPS) and has experience fundraising for the College of Lake County (CLC). He helped set a record amount of donations at the 2016 CLC Foundation Gala, where he was an invited speaker and volunteer. He will be attending the ANS National conference in November 2019, as well as the ANS Student Conference 2020 at North Carolina State University.\\

\setlength\intextsep{0pt}
\begin{wrapfigure}{R}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[height=15\baselineskip]{mettlerj.jpg}
	\end{center}
\end{wrapfigure}
$\textbf{Technical Co-Chair - Jeremy Mettler}$\\
Jeremy graduated with a B.S. in Nuclear, Plasma, and Radiological Engineering from UIUC in 2018, and is now attending as a 2nd-year graduate student studying plasma science under Dr. David Ruzic. He has been heavily involved in the UIUC student chapter of ANS since his freshman year, serving on the executive board for three years as External Vice President and President. Jeremy has attended the past five ANS Student Conferences, which serve as an inspiration for his involvement in this proposal process. He is dedicated to making sure that future generations of students are able to have the same amazing experiences through ANS as he had, especially at the ANS Student Conference. Outside of ANS, he has held a summer internship at Oak Ridge National Lab, and is currently focusing his research towards combined laser-plasma systems for materials processing.\\

### 2019-09-23 proglog.tex
adds hotel info and jeremy bio

>>>>

% =========================================================================================
% =========================================================================================
% =========================================================================================
% Technical and Non-Technical Tours
% =========================================================================================
% =========================================================================================
% =========================================================================================

\subsection{Tours}

\subsubsection{Technical Tours}
Out of the 61 commercially operating nuclear power plants and 99 nuclear reactors in the U.S., Illinois is home to six nuclear power stations and eleven active reactors. Being located in a state with numerous power plants, as well as being surrounded by locations of interest to a variety of nuclear-related disciplines, the touring opportunities at the University of Illinois mirror the diversity of UIUC’s Nuclear Plasma and Radiological Engineering program.\\

\textbf{Argonne National Laboratory}\\
Located in Lemont, Illinois, Argonne works closely with universities, industry, and other national labs to help make an impact on the atomic, human, and global scale. With 14 research divisions, five national scientific user facilities, and hundreds of research partners, attendees of this tour will be exposed to the diverse areas of research in nuclear science. Argonne is two-and-a-half-hour drive away. Bus transportation will be provided. On the tour, students will be guided around the site’s scientific and engineering facilities.\\

\textbf{Clinton Power Station}\\
Located about 35 miles away from Champaign, the Clinton Power Station is an Exelon owned nuclear power plant that started operating at full power on September 15th, 1987. They currently serve over one million customers and operate 94.9$\%$ of the time. The tour will be held on Thursday morning and bus transportation will be provided. Attendees will be guided by a Clinton employee. The tour will include the control-room simulator that operator trainees use, and a chance to learn more about the site’s innovative safety, operation, and engineering practices.\\

\textbf{Starfire Industries LLC}\\
Starfire Industries is located at the south end of campus and works with federal organizations such as DARPA, Homeland Security, NASA, and others. They offer services in areas like neutron radiography, fabrication, and prototyping. Students will be able to get to the site by using the MTD busses that run continuously throughout the day and will be free to all conference attendees. Here, students will be able to learn more about Starfire products such as the IMPULSE pulsed power module, plasma sources, thin film systems, nGen neutron generators, neutron detectors, and the PICTORIS neutron radiography system. Starfire’s collaboration with government agencies and propensity for solving big problems related to plasma engineering make them a great place to learn about plasma processing applications.\\

\textbf{National Center for Supercomputing Applications (NCSA)}\\
Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world. The NCSA is within walking distance from all conference hotels. During the tour, attendees will tour the machine room and witness some of the beautiful results it produces. Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.\\

\subsubsection{Non-Technical Tours}

Brewery tours are staple social event and tour at the ANS Student Conference. Champaign-Urbana has several popular local breweries that give tours and tastings at their facilities. Due to this, we will be able to expand the number of attendees that can go on these tours over previous conferences. These will require sign up before the conference and we expect spots to fill up quickly.\\

\textbf{Riggs Brewery Tour}\\
For 21+ attendees, two tours of a local brewery will be included in our tours list Thursday afternoon from 3-5pm. Find out how Riggs makes their beer and taste test it along the way. Each tour will last approximately one hour and accommodates up to 20 people per tour. Riggs is located in east Urbana. Transportation to and from the brewery will be provided. \\

\textbf{Triptych Brewery Tour}\\
For 21+ attendees, Triptych offers two tours that run around 1.5 hours for roughly 30 people each that includes several beer tastings throughout. Tours will be from 2-5pm on Thursday afternoon. Triptych is located in Savoy, IL, just 15 minutes from campus. Transportation to and from the brewery will be provided.\\

\textbf{University Tour}\\
Attendees will be able to take a tour of the UIUC campus. They will start at the Talbot Laboratory where the department of Nuclear Plasma and Radiological Engineering is located. Here, students will get to see the Virtual Education and Research Laboratory to see how virtual reality technology can be adapted and applied to educational methods. There are also many other historical artifacts on display for participants to see. Afterwards, students will be led to various noteworthy locations unique to UIUC.\\
